Symbolic Weighted Language Models and\\ Parsing over Infinite Alphabets

### 2021-07-05 introduction.tex
Commentaires Philippe

% !TEX root = main.tex
%\todo
% Introduction
%
Parsing %variant of membership problem for formal languages
%- given a language model and an input word $s$, compute a derivation of the model that yields $s$.
is the problem %process 
of structuring a linear representation on input %typically
(a finite word), according to a language model. % (a formal grammar).
% natural language, programming language, 
%
Most of the context-free parsing approaches~\cite{GruneJacobs08parsing}  
assume a finite and reasonably small input alphabet. %models and algorithms 
Such a restriction makes perfect sense in the context of NLP tasks such as constituency parsing,
or of programming languages compilers or interpreters.
Considering large or infinite alphabets can however be of practical interest, %in other cases.
%
for instance, when dealing with large characters encodings such as UTF-16, % processing strings in 
\eg for vulnerability detection in Web-applications~\cite{dAntoni21CACM}, 
%
for the analyse (\eg validation or filtering) 
of data streams or serialization of structured documents 
(with textual or numerical attributes)~\cite{Segoufin06csl}, 
or for processing timed execution traces~\cite{Bouyer03algebraic}.
% algebraic definition of a class of data languages 
% (notion of monoid recognizability, based on registers, comparable to Bojancszik et al. data words)
%
The latter case is related to a study that motivated the present work: 
automated music transcription.
In this problem, a music performance, % a symbolic representation of a music performance 
represented symbolically in the form of a sequence of timed musical events, % timestamped
is converted into a score in Common Western Music Notation~\cite{Gould11Notation},
structured according to nested grouping and metric strength of events.
%(the structure represents hierarchical  grouping of events, and their relative temporal positions)
It can therefore be stated as a parsing problem~\cite{foscarin:hal-01988990}, 
over an infinite alphabet of timed events.

>>>>

% !TEX root = main.tex
%\todo
% Introduction
%
Parsing %variant of membership problem for formal languages
%- given a language model and an input word $s$, compute a derivation of the model that yields $s$.
is the problem %process 
of structuring a linear representation on input %typically
(a finite word), according to a language model. % (a formal grammar).
% natural language, programming language, 
%
Most of the context-free parsing approaches~\cite{GruneJacobs08parsing}  
assume a finite and reasonably small input alphabet. %models and algorithms 
Such a restriction makes perfect sense in the context of NLP tasks such as constituency parsing,
or of programming languages compilers or interpreters.
Considering large or infinite alphabets can however be of practical interest, %in other cases.
%
for instance, when dealing with large characters encodings such as UTF-16, % processing strings in 
\eg for vulnerability detection in Web-applications~\cite{dAntoni21CACM}, 
%
for the analyse (\eg validation or filtering) 
of data streams or serialization of structured documents 
(with textual or numerical attributes)~\cite{Segoufin06csl}, 
or for processing timed execution traces~\cite{Bouyer03algebraic}.
% algebraic definition of a class of data languages 
% (notion of monoid recognizability, based on registers, comparable to Bojancszik et al. data words)
%
The latter case is related to a study that motivated the present work: 
automated music transcription.
\mynote{I think that we can make the case for a larger set of situations: given a linear 
music notation input, for instance elements in an XML file, we we want to structure
the input according to a hierarchical rhythmic space. I can elaborate...}
In this problem, a music performance, % a symbolic representation of a music performance 
represented symbolically in the form of a sequence of timed musical events, % timestamped
is converted into a score in Common Western Music Notation~\cite{Gould11Notation},
structured according to nested grouping and metric strength of events.
%(the structure represents hierarchical  grouping of events, and their relative temporal positions)
It can therefore be stated as a parsing problem~\cite{foscarin:hal-01988990}, 
over an infinite alphabet of timed events.
